\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage[english]{babel}
\input{glyphtounicode}

% Formatting
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\pdfgentounicode=1
\raggedbottom
\raggedright

% Section formatting
\titleformat{\section}{\scshape\large\raggedright}{}{0em}{}[\titlerule]

% Custom Commands
\newcommand{\resumeItem}[1]{\item \small{#1}}
\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}
}
\newcommand{\resumeSectionStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSectionEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
\begin{document}

%----------HEADER----------
\begin{center}
  \textbf{\Huge Pham Tien Dat} \\ \vspace{1pt}
  Software Engineer Intern \\ \vspace{1pt}
  \href{mailto:dat20036@gmail.com}{dat20036@gmail.com} $|$
  +84 335-693-042 $|$
  \href{https://github.com/swyrin}{github.com/swyrin} $|$
  \href{https://linkedin.com/in/tiendatpham2077}{linkedin.com/in/tiendatpham2077}
\end{center}

%----------SUMMARY----------
\section*{Summary}
Full-Stack Software Engineer with hands-on experience developing scalable web applications using modern technologies across the stack. Proficient in React, TypeScript, Tailwind CSS, and Next.js on the front end, and Node.js, Python, ASP.NET Core, and Prisma on the back end. Skilled in building RESTful APIs, integrating databases, and managing DevOps workflows. Committed to writing clean, maintainable code and collaborating effectively in team-driven environments.

%----------SKILLS----------
\section*{Technical Skills}
\resumeSectionStart
  \item \textbf{Languages:} Python, Java, C\#, TypeScript, Rust, SQL, C/C++
  \item \textbf{Frameworks / Libraries:} ASP.NET Core, Spring Boot, Axum, Prisma, React, TailwindCSS, Next.js
  \item \textbf{Tools:} Git, Docker, Nginx, DBeaver, Visual Studio Code, Rider, WebStorm, Vite
  \item \textbf{Databases:} MySQL, PostgreSQL, MongoDB
  \item \textbf{Concepts:} RESTful APIs, CI/CD, Object-Oriented Design, Meta-programming
\resumeSectionEnd

%----------EDUCATION----------
\section*{Education}
\resumeSectionStart
  \resumeSubheading
    {International University - VNU HCMC}{Ho Chi Minh City}
    {B.Eng. in Information Technology, GPA: 3.32 / 4.0}{Sep 2021 -- Present}
\resumeSectionEnd

%----------EXPERIENCE----------
\section*{Experience}
\resumeSectionStart
  \resumeSubheading
    {Problem Setter}{2022}
    {\href{https://luyencode.net}{LC Online Judge}}{\href{https://luyencode.net}{https://luyencode.net}}
  \resumeItemListStart
    \resumeItem{Designed algorithmic problems across difficulty levels for national programming competitions.}
    \resumeItem{Collaborated with setters to improve problem quality and balance challenge.}
  \resumeItemListEnd

  \resumeSubheading
    {Teaching Assistant (C/C++ Programming, Calculus 1)}{Q1 2023}
    {\href{https://www.hcmiu.edu.vn}{International University}}{Ho Chi Minh City}
  \resumeItemListStart
    \resumeItem{Prepared structured post-lecture study materials and hosted virtual review sessions.}
    \resumeItem{Supported midterm/final exam prep for 100+ students.}
  \resumeItemListEnd

  \resumeSubheading
    {Event Coordinator / IT Lead}{Q4 2024}
    {\href{https://www.facebook.com/terrastationvn}{Arknights Vietnam Station}}{\href{https://www.facebook.com/terrastationvn}{Facebook: terrastationvn}}
  \resumeItemListStart
    \resumeItem{Led technical execution for interactive event microsite using Next.js and Netlify.}
    \resumeItem{Increased engagement via gamified features and real-time event updates.}
  \resumeItemListEnd
\resumeSectionEnd

%----------PROJECTS----------
\section*{Projects}
\resumeSectionStart
  \resumeSubheading
    {Nameless* (Lead Developer)}{2020 -- Present}
    {Python, Prisma, Ruff, uv}{\href{https://github.com/team-nameless/nameless-discord-bot}{github.com/team-nameless/nameless-discord-bot}}
  \resumeItemListStart
    \resumeItem{Built Discord bot with Python meta-programming and async features.}
    \resumeItem{Used Ruff and uv for efficient builds and linting.}
  \resumeItemListEnd

  \resumeSubheading
    {Arknights Vietnam Web (Lead Dev)}{Q4 2024 -- Present}
    {Next.js, Prisma, MongoDB, Netlify}{\href{https://github.com/Arknights-Vietnam-Station/the-web}{github.com/Arknights-Vietnam-Station/the-web}}
  \resumeItemListStart
    \resumeItem{Architected SSG + SSR website with Next.js App Router and Prisma ORM.}
    \resumeItem{Deployed via Netlify with CI integration for GitHub and Discord webhooks.}
    \resumeItem{Built API endpoints for event interactions and draft system.}
  \resumeItemListEnd

  \resumeSubheading
    {Starlight (Backend/Game Dev)}{Q4 2024}
    {ASP.NET Core, EF Core, MySQL, Phaser.js}{\href{https://github.com/swyrin/starlight}{github.com/swyrin/starlight}}
  \resumeItemListStart
    \resumeItem{Developed backend using Identity, EF Core, and controller-based REST APIs.}
    \resumeItem{Created Phaser.js front-end game logic interfaced with backend via React + Axios.}
    \resumeItem{Documented APIs with Swagger; used CORS policies for access control.}
  \resumeItemListEnd
\resumeSectionEnd

%----------ACHIEVEMENTS----------
\section*{Achievements}
\resumeSectionStart
  \resumeSubheading
    {Excellent Student Award (3rd Place - Informatics)}{June 2021}
    {\href{https://moet.gov.vn}{Ministry of Education and Training}}{Vietnam}
  \resumeItemListStart
    \resumeItem{Solved C++ algorithmic problems under timed conditions at city level.}
  \resumeItemListEnd

  \resumeSubheading
    {Semester Scholarship (600 USD)}{2022}
    {\href{https://hcmiu.edu.vn}{International University - VNU HCMC}}{Vietnam}
  \resumeItemListStart
    \resumeItem{Earned GPA of 3.76/4.0 during awarded semester.}
  \resumeItemListEnd

  \resumeSubheading
    {IELTS 7.0 (English Proficiency)}{Sep 2024}
    {\href{https://ielts.idp.com}{IDP Ho Chi Minh (VN101)}}
    {Vietnam}
  \resumeItemListStart
    \resumeItem{Detailed scoring: Reading 8.0, Listening 9.0, Speaking 5.5, Writing 6.5}
  \resumeItemListEnd
\resumeSectionEnd


\end{document}
